intro

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hyp. 6
comments on Hyp. 6a and 6b

We also want to investigate whether SVs are related to flexible emotion regulation:

* H6a) The higher the SV, the more likely the respective strategy is chosen.
* H6b) SVs are lower and decline stronger when ER flexibility is lower.

>>>>

We also want to investigate whether SVs are related to flexible emotion regulation: <!-- Denise: Ihr habt ER Flex schon im Theoretischen Hintergrund eingeführt, aber mir fehlt noch bischen der differentielle Aspekt, den ihr ja hier untersuchen wollt. Ich versuche, dies mal oben reinzuformulieren. -->

* H6a) The higher the SV, the more likely the respective strategy is chosen. <!-- warum ist diese Hyp. hier bei ER Flexbility?-->
* H6b) SVs are lower and decline stronger when ER flexibility is lower.

<!-- Denise: Hyp. 6b Was heißt "decline stronger?" Meint ihr "decline stronger with increasing effort" oder "decline from strategy A to stratey B"? Mein Problem ist, dass ich immer noch nicht 100% durch das ERED Paradigma durchsteige und die Auswertung der SVs auch noch nicht 100% verstehe. Das liegt nicht unbedingt an eurem Methodenteil, aber eventuell muss das noch etwas ausführlicher beschrieben werden. Da es anderen Reviewers ja auch so gehen könnte.-->
